---
title: "p8105_hw4_p2"
author: "Yeyi Zhang"
date: "10/25/2017"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(tidyverse)
library(janitor)
library(ggthemes)
```

1. Load and tidy the `pols-month.csv` and `GDP.csv` from fivethirtyeight datasets.

```{r }
pols = read_csv("./data/fivethirtyeight_datasets/pols-month.csv") %>% 
  clean_names()

gdp = read_csv("./data/fivethirtyeight_datasets/GDP.csv") %>% 
  clean_names()
```

2. Combine the two sets based on the `date` / `month`.

```{r combine}
pols_tidy = pols %>% 
  mutate(mon = lubridate::floor_date(mon, "month")) %>% 
  rename(date = mon)

data_combine = left_join(pols_tidy, gdp)
```

3. Create a plot showing the GDP value over time, including the party of the president.

```{r setup_plot}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r plot}
data_combine %>% 
  filter(value != ".", !is.na(value)) %>%
  separate(col = date, into = c("year", "month", "day")) %>%
  mutate(value = as.numeric(value),
         year = as.numeric(year),
         president_party = as.character(prez_dem),
         president_party = recode(president_party, "1" = "Democratic", "0" = "Republican")) %>% 
  group_by(year, president_party) %>% 
  summarize(mean_yr = mean(value)) %>% 
  ggplot(aes(x = year, y = mean_yr, color = president_party, fill = president_party)) +
    geom_col(aes(group = president_party)) +
  labs(
    title = "GDP Value over Year",
    x = "Year",
    y = "GDP Value",
    caption = "Data from 538 dataset"
  ) +
  theme_bw()
```

3. Make conclusions of the results.
* The value of __GDP__ went up before 1970s and decreasing afterwards.
* The party of the presidents actually had effects on __GDP__ values, according to the plot.